target_offtarget

### 2025-01-21 manuscript_figures.Rmd
updating figures

read_count_dedup <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(
    x = Viral.load,
    y = log(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10() +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("Log(Viral Reads)")

@@

read_count_norm2_dedup <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(
    x = Viral.load,
    y = log(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10() +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("Log(viral reads/cleaned reads/genome length)")

@@

ggsave("figures/compare_spike_ins_atcc/log_read_count_depth_2panels_dedup.png",
       width=10,
       height=7)

ggsave("figures/manuscript_figures_pdf/Figure1.pdf",
       width=10,
       height=7)

@@

@@

ggsave(
  "figures/manuscript_figures_pdf/Figure_2.pdf",
  width = 15,
  height = 6
)

@@

### Figure S5 - linear model
```{r}
#Linear model for TE data - separated by virus
#November 2024

rm(list = ls())

library(tidyverse)
library(broom)

#all viruses together

rsq <- function (x, y)
  cor(x, y) ^ 2

virus <- (unique(depths_reads_sub$virus)) |>
  rep(., each = 2) |>
  data.frame()

>>>>

read_count_dedup <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(
    x = Viral.load,
    y = log(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10() +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("Log(Viral Reads)") +
  xlab("Viral load")

@@

read_count_norm2_dedup <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(
    x = Viral.load,
    y = log(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_x_log10() +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  ylab("Log(viral reads/cleaned reads/genome length)") +
  xlab("Viral load")

@@

# ggsave("figures/compare_spike_ins_atcc/log_read_count_depth_2panels_dedup.png",
#        width=10,
#        height=7)

ggsave("figures/manuscript_figure_2025/PDF/Figure_1.pdf",
       width=6,
       height=8)

ggsave("figures/manuscript_figure_2025/PNG/Figure_1.png",
       width=6,
       height=8)

@@

### Figure S5 - linear model

#### Read-in data
```{r}
#Linear model for TE data - separated by virus
#November 2024

library(tidyverse)
library(broom)
library(boot)

#### Format data
```{r}

#### model
```{r}
#all viruses together

rsq <- function (x, y) {
  cor(x, y) ^ 2
}

virus <- (unique(depths_reads_sub$virus)) |>
  rep(each = 2) |>
  data.frame() |>
  rename(virus = rep..unique.depths_reads_sub.virus....each...2.)

@@

ggsave(
  "figures/manuscript_figure_2025/PDF/Figure_2.pdf",
  width = 15,
  height = 6
)

ggsave(
  "figures/manuscript_figure_2025/PNG/Figure_2.png",
  width = 15,
  height = 6
)

@@
